\bf{Commonality Analysis for Lattice Boltzmann Systems}

### 2020-04-01 StateOfPractice/Peter-Notes/Commonality-Analysis-LB-Systems.tex
commonality analysis for LB

\begin{titlepage}
	\clearpage\maketitle
	\thispagestyle{empty}
	\begin{abstract}
		This report presents a commonality analysis for Lattice Boltzmann systems. The document reviews both the methodology of commonality analysis and the details of Lattice Boltzmann systems. The commonality analysis itself consists of the following:
		i) terminology and definitions; ii) commonalities, or features that are common to all potential family members; iii) variabilities, or features and characteristics that may vary among family members; and, iv) parameters of variation, or the potential values that can be assigned to the variabilities. 
		The documentation of the above items for Lattice Boltzmann systems is clarified by decomposing each item into subsections on Lattice Boltzmann methods, input, output, nonfunctional
		requirements, and, where appropriate, system constraints.\\

@@

\section{Introduction}
Mesh generating systems are well suited to development as a program family because they
fit Parnas’s definition of a program family: “a set of programs whose common properties
are so extensive that it is advantageous to study the common properties of the programs
before analyzing individual members” (Parnas, 1976). Developing mesh generating sys-
tems as a program family is advantageous because mesh generators share many common
features, or commonalities. Furthermore, when there are differences between systems, the
variabilities between them can be systematically considered. The purpose of this document
is to record these commonalities and variabilities and show the relationships between them,
and thus facilitate the specification and development of mesh generator program family
members. This document will be valuable in all future phases of system development and
analysis. For instance, the requirements documentation for any mesh generator will use
the commonality analysis, since the requirements should refine the commonalities, which
are shared requirements of all mesh generators. Moreover, the design of any future system
will use this documentation to facilitate consideration of the variabilities, so that likely
changes can be made to the system with a minimal amount of work.
The scope of the commonality analysis presented here can be considered both from the
point of view of mesh generating systems and from the point of view of software engineering
methodologies. From the mesh generator perspective, the starting point for the current
document is the commonality analysis conducted by Chen (2003). However, the scope of
the current document is broader than that of Chen (2003), which was restricted to two-
dimensional meshes and did not consider non-conformal, hybrid or mixed meshes. The
current commonality analysis is intended to cover all mesh generators that are targeted
at finite element applications. Meshes for cartography or other uses are not explicitly
considered, although much of the information in this document does overlap with other
mesh uses. With respect to software engineering methodologies, the scope of the current
report is restricted to informal methods, with the intention that the informal requirements
will form a starting point for later development and refinement by formal methods.
The first section below provides an overview of the program family of mesh generators,
by reviewing what is involved in a commonality analysis and the basics of mesh generating
systems. After this, the basic terminology and definitions necessary for understanding the
remainder of the document are provided. The definitions include terms used in describing
a commonality analysis and terms that are used in defining the characteristics and prop-
erties of meshes. The next three sections consist of the lists of commonalities, variabilities
and parameters of variation, respectively. These three sections form the heart of the docu-
mentation and include an extensive set of cross-references to demonstrate the relationships
between the different items. The final section provides information on unresolved issues.

\newpage
\section{Overview}
This section provides both an overview of the process of commonality analysis and of mesh
generation. The subsection on commonality analysis briefly introduces this topic, along
with references that can be searched for further information. The subsection on mesh
generators outlines the following: i) the basics of mesh generation, ii) the scope of the
current analysis, iii) the overall philosophy that has been adopted for the commonality
analysis, and iv) the arguments in favour of the development of mesh generators as a
program family.

\subsection{Commonality Analysis}
In some situations it is advantageous to develop a collection of related software products
as a program family. The idea is that if the software products are similar enough, then
it should be possible to predict what the products have in common, what differs between
them and then reuse the common aspects and thus support rapid development of the
family members. The idea of program families was introduced by Dijkstra (1972) and later
investigated by Parnas (Parnas, 1976, 1979). More recently, Weiss (Weiss, 1997, 1998;
Ardis and Weiss, 1997) has considered the concept of a program family in the context of
what he terms Family oriented Abstraction, Specification and Translation (FAST) (Cuka
and Weiss, 1997; Weiss and Lai, 1999).
In the approach advocated by Weiss, the first step is a commonality analysis. This
analysis consists of systematically identifying and documenting the commonalities that all
program family members share, the variabilities between family members and the termi-
nology used in describing the family. A commonality analysis provides a systematic way of
gaining confidence that a family is worth building and of deciding what the family members
will be. A commonality analysis document provides the following benefits (Weiss, 1997,
1998):
1. A starting point for the design of a domain specific languages (DSL): Once a DSL,
or application modelling language, is developed the program family members can be
rapidly generated by specifying a given family member using the language.
2. A basis for a common design for all family members: When the software engineers
come to designing the individual family members, they can take advantage of the
commonalities to reuse code. Moreover, the variabilities can be considered in the
design so that they can be easily accommodated. One approach to the design may
be to decompose the system into components that can each be customized by speci-
fication of values for its various parameters, where the parameters correspond to the
parameters of variation identified in the commonality analysis document.
3. A historical reference: This document records the important issues concerning the
scope and the nature of the family (as well as some unsolved issues) to facilitate the
involvement of the participants in maintaining and evolving the family.
CAS-04-10-SS
4
4. A basis for reengineering a domain: Existing projects may not have been developed
using software engineering methodologies. The projects can be systematically reor-
ganized and redesigned with the aid of a commonality analysis to unify the existing
products.
5. A basic training reference for new software developers: This document provides the
necessary basic information for a new team-member to understand the family.
The next section will show that the above uses of the commonality analysis document
will be beneficial for the development of a program family of mesh generators. The com-
monality analysis will benefit all subsequent stages in the software development process.
For instance, as mentioned in the introduction, the commonalities will act as requirements
that will be the starting point for writing a software requirements specification. The com-
monalities will be refined into specific requirements by fixing the value of their associated
variabilities. The change in the values of the variabilities then corresponds to the change
from one program family member to another.
As commonalities and variabilities are requirements, they should express “What” func-
tionalities and qualities the system should have, and not mention “How” these requirements
are to be accomplished. That is, the commonalities and variabilities should not involve
design decisions. The design decisions will be made after the requirements for a family
member have been specified. The one exception to this is system constraints, which are
requirements that explicitly make design decisions.
Besides the “What” versus “How” test, there are other tests that can be used to review
commonalities and variabilities, as proposed by Weiss (1997). One such test is the “what
is ruled out” test. This test determines if a commonality or variability actually makes a
decision because if no alternatives are ruled out then no decision has really been made.
Another test is the “negation” test. If the negation of a decision represents a position
that someone might argue for, then the original decision is likely to be meaningful. For
instance, the statement that “the software should be reliable” has a negation that no one
would likely argue for and thus the statement does not represent a good characterization
of a goal for the system.
In Weiss (1997) the stages of a commonality analysis are described in a systematic way.
The stages include the following: prepare, plan, analyze, quantify and review. The stages
are completed through the aid of a moderator and a series of meeting and preliminary
documents and documentation reviews. Although the systematic approach advocated by
Weiss has its advantages, for the case of writing a commonality analysis document for mesh
generating systems it was decided that a less structured approach is feasible. Mesh genera-
tors are simpler than other software systems in the sense that they have fewer interactions
with the environment. Also, the theory of mesh generation has a solid mathematical ba-
sis that can be used to remove some of the ambiguity that Weiss’s approach is aimed
at reducing. Therefore, the approach adopted here is to revise the original commonality
analysis document produced by Chen (2003) and then make the new document available
to others for review. The new document will be maintained in a concurrent versioning
CAS-04-10-SS
5
system repository so that multiple authors can work on it, and more importantly, so that
the documentation’s revision history can be tracked and the documentation can be rolled
back to an earlier version if necessary.

\subsection{Lattice Boltzmann Systems}
\newpage
\section{Terminology and Definitions}
This section is divided into two subsections. The first discusses the terminology that comes
from the software engineering field, while the second presents the definitions used in mesh
generation. Common acronyms are also listed in this section. The lists are not intended
to be read sequentially, but rather to be consulted for reference purposes; therefore, the
terms are ordered alphabetically, with the consequence that some terms that appear early
in the list depend on the definitions of later terms.

\subsection{Software Engineering Related Definitions and Acronyms}
Commonality: A requirement or goal common to all family members.
Goal: “Goals capture, at different levels of abstraction, the various objectives the system
under consideration should achieve.” van Lamsweerde (2001)
Program Family: A set of programs that are analyzed and designed together starting
from the initial stages of the software development life-cycle.
Requirements: A software requirement is: i) a condition or capability needed by a user
to solve a problem or achieve an objective; ii) a condition or capability that must be
met or possessed by a system or system component to satisfy a contract, standard,
specification, or other formally imposed document; or, iii) a documented represen-
CAS-04-10-SS
10
tation of a condition or capability as in the above two definitions.
Dorfman, 2000)
Variability: A requirement or goal that varies between family members.
\subsection{Lattice Boltzmann Related Definitions and Acronyms}
\newpage
\section{Commonalities}
\subsection{Lattice Boltzmann Method Solvers}
\noindent
\begin{minipage}{\textwidth}
	\renewcommand*{\arraystretch}{1.5}
	\begin{tabular}{| p{\colAwidth} | p{\colBwidth}|}
		\hline
		\bf Item Number& C\refstepcounter{comnum}\thecomnum \\
		\hline
	\end{tabular}\\

	\begin{tabular}{| p{\colAwidth} | p{\colBwidth}|}		
		\hline
		\bf Description & \\
		\hline
		\bf Related Variability & \vref{}\\
		\hline
		\bf History & \\
		\hline
	\end{tabular}
\end{minipage}\\
~\newline\\
~\newline
\noindent
\begin{minipage}{\textwidth}
	\renewcommand*{\arraystretch}{1.5}
	\begin{tabular}{| p{\colAwidth} | p{\colBwidth}|}
		\hline
		\bf Item Number& C\refstepcounter{comnum}\thecomnum \\
		\hline
	\end{tabular}\\

	\begin{tabular}{| p{\colAwidth} | p{\colBwidth}|}		
		\hline
		\bf Description & \\
		\hline
		\bf Related Variability & \vref{}\\
		\hline
		\bf History & \\
		\hline
	\end{tabular}
\end{minipage}\\
\subsection{Input}
\noindent
\begin{minipage}{\textwidth}
	\renewcommand*{\arraystretch}{1.5}
	\begin{tabular}{| p{\colAwidth} | p{\colBwidth}|}
		\hline
		\bf Item Number& C\refstepcounter{comnum}\thecomnum \\
		\hline
	\end{tabular}\\

	\begin{tabular}{| p{\colAwidth} | p{\colBwidth}|}		
		\hline
		\bf Description & \\
		\hline
		\bf Related Variability & \vref{}\\
		\hline
		\bf History & \\
		\hline
	\end{tabular}
\end{minipage}\\
~\newline\\
~\newline
\noindent
\begin{minipage}{\textwidth}
	\renewcommand*{\arraystretch}{1.5}
	\begin{tabular}{| p{\colAwidth} | p{\colBwidth}|}
		\hline
		\bf Item Number& C\refstepcounter{comnum}\thecomnum \\
		\hline
	\end{tabular}\\

	\begin{tabular}{| p{\colAwidth} | p{\colBwidth}|}		
		\hline
		\bf Description & \\
		\hline
		\bf Related Variability & \vref{}\\
		\hline
		\bf History & \\
		\hline
	\end{tabular}
\end{minipage}\\
\subsection{Output}
\noindent
\begin{minipage}{\textwidth}
	\renewcommand*{\arraystretch}{1.5}
	\begin{tabular}{| p{\colAwidth} | p{\colBwidth}|}
		\hline
		\bf Item Number& C\refstepcounter{comnum}\thecomnum \\
		\hline
	\end{tabular}\\

	\begin{tabular}{| p{\colAwidth} | p{\colBwidth}|}		
		\hline
		\bf Description & \\
		\hline
		\bf Related Variability & \vref{}\\
		\hline
		\bf History & \\
		\hline
	\end{tabular}
\end{minipage}\\
~\newline\\
~\newline
\noindent
\begin{minipage}{\textwidth}
	\renewcommand*{\arraystretch}{1.5}
	\begin{tabular}{| p{\colAwidth} | p{\colBwidth}|}
		\hline
		\bf Item Number& C\refstepcounter{comnum}\thecomnum \\
		\hline
	\end{tabular}\\

	\begin{tabular}{| p{\colAwidth} | p{\colBwidth}|}		
		\hline
		\bf Description & \\
		\hline
		\bf Related Variability & \vref{}\\
		\hline
		\bf History & \\
		\hline
	\end{tabular}
\end{minipage}\\
\subsection{Nonfunctional Requirements}
\noindent
\begin{minipage}{\textwidth}
	\renewcommand*{\arraystretch}{1.5}
	\begin{tabular}{| p{\colAwidth} | p{\colBwidth}|}
		\hline
		\bf Item Number& C\refstepcounter{comnum}\thecomnum \\
		\hline
	\end{tabular}\\

	\begin{tabular}{| p{\colAwidth} | p{\colBwidth}|}		
		\hline
		\bf Description & \\
		\hline
		\bf Related Variability & \vref{}\\
		\hline
		\bf History & \\
		\hline
	\end{tabular}
\end{minipage}\\
~\newline\\
~\newline

\noindent
\begin{minipage}{\textwidth}
	\renewcommand*{\arraystretch}{1.5}
	\begin{tabular}{| p{\colAwidth} | p{\colBwidth}|}
		\hline
		\bf Item Number& C\refstepcounter{comnum}\thecomnum \\
		\hline
	\end{tabular}\\

	\begin{tabular}{| p{\colAwidth} | p{\colBwidth}|}		
		\hline
		\bf Description & \\
		\hline
		\bf Related Variability & \vref{}\\
		\hline
		\bf History & \\
		\hline
	\end{tabular}
\end{minipage}\\
\newpage
\section{Variabilities}
\subsection{Lattice Boltzmann Method Solvers}
\noindent
\begin{minipage}{\textwidth}
	\renewcommand*{\arraystretch}{1.5}
	\begin{tabular}{| p{\colCwidth} | p{\colDwidth}|}
		\hline
		\bf Item Number& V\refstepcounter{varnum}\thevarnum \\
		\hline
	\end{tabular}\\

	\begin{tabular}{| p{\colCwidth} | p{\colDwidth}|}		
		\hline
		\bf Description & \\
		\hline
		\bf Related Commonality & \cref{}\\
		\hline
		\bf Related Parameter & \pref{}\\
		\hline
		\bf History & \\
		\hline
	\end{tabular}
\end{minipage}\\
~\newline\\
~\newline
\noindent
\begin{minipage}{\textwidth}
	\renewcommand*{\arraystretch}{1.5}
	\begin{tabular}{| p{\colCwidth} | p{\colDwidth}|}
		\hline
		\bf Item Number& V\refstepcounter{varnum}\thevarnum \\
		\hline
	\end{tabular}\\

	\begin{tabular}{| p{\colCwidth} | p{\colDwidth}|}		
		\hline
		\bf Description & \\
		\hline
		\bf Related Commonality & \cref{}\\
		\hline
		\bf Related Parameter & \pref{}\\
		\hline
		\bf History & \\
		\hline
	\end{tabular}
\end{minipage}\\
\subsection{Input}
\noindent
\begin{minipage}{\textwidth}
	\renewcommand*{\arraystretch}{1.5}
	\begin{tabular}{| p{\colCwidth} | p{\colDwidth}|}
		\hline
		\bf Item Number& V\refstepcounter{varnum}\thevarnum \\
		\hline
	\end{tabular}\\

	\begin{tabular}{| p{\colCwidth} | p{\colDwidth}|}		
		\hline
		\bf Description & \\
		\hline
		\bf Related Commonality & \cref{}\\
		\hline
		\bf Related Parameter & \pref{}\\
		\hline
		\bf History & \\
		\hline
	\end{tabular}
\end{minipage}\\
~\newline\\
~\newline
\noindent
\begin{minipage}{\textwidth}
	\renewcommand*{\arraystretch}{1.5}
	\begin{tabular}{| p{\colCwidth} | p{\colDwidth}|}
		\hline
		\bf Item Number& V\refstepcounter{varnum}\thevarnum \\
		\hline
	\end{tabular}\\

	\begin{tabular}{| p{\colCwidth} | p{\colDwidth}|}		
		\hline
		\bf Description & \\
		\hline
		\bf Related Commonality & \cref{}\\
		\hline
		\bf Related Parameter & \pref{}\\
		\hline
		\bf History & \\
		\hline
	\end{tabular}
\end{minipage}\\
\subsection{Output}
\noindent
\begin{minipage}{\textwidth}
	\renewcommand*{\arraystretch}{1.5}
	\begin{tabular}{| p{\colCwidth} | p{\colDwidth}|}
		\hline
		\bf Item Number& V\refstepcounter{varnum}\thevarnum \\
		\hline
	\end{tabular}\\

	\begin{tabular}{| p{\colCwidth} | p{\colDwidth}|}		
		\hline
		\bf Description & \\
		\hline
		\bf Related Commonality & \cref{}\\
		\hline
		\bf Related Parameter & \pref{}\\
		\hline
		\bf History & \\
		\hline
	\end{tabular}
\end{minipage}\\
~\newline\\
~\newline
\noindent
\begin{minipage}{\textwidth}
	\renewcommand*{\arraystretch}{1.5}
	\begin{tabular}{| p{\colCwidth} | p{\colDwidth}|}
		\hline
		\bf Item Number& V\refstepcounter{varnum}\thevarnum \\
		\hline
	\end{tabular}\\

	\begin{tabular}{| p{\colCwidth} | p{\colDwidth}|}		
		\hline
		\bf Description & \\
		\hline
		\bf Related Commonality & \cref{}\\
		\hline
		\bf Related Parameter & \pref{}\\
		\hline
		\bf History & \\
		\hline
	\end{tabular}
\end{minipage}\\
\subsection{System Constraints}
\noindent
\begin{minipage}{\textwidth}
	\renewcommand*{\arraystretch}{1.5}
	\begin{tabular}{| p{\colCwidth} | p{\colDwidth}|}
		\hline
		\bf Item Number& V\refstepcounter{varnum}\thevarnum \\
		\hline
	\end{tabular}\\

>>>>

\begin{titlepage}
	\clearpage\maketitle
	\thispagestyle{empty}
	\begin{abstract}
		This report presents a commonality analysis for Lattice Boltzmann systems using a commonality analysis template based on \cite{SmithAndChen2004}. The document reviews both the methodology of commonality analysis and the details of Lattice Boltzmann systems. The commonality analysis itself consists of the following:
		\textit{i}) terminology and definitions; \textit{ii}) commonalities, or features that are common to all potential family members; \textit{iii}) variabilities, or features and characteristics that may vary among family members; and, \textit{iv}) parameters of variation, or the potential values that can be assigned to the variabilities. 
		The documentation of the above items for Lattice Boltzmann systems is clarified by decomposing each item into subsections on Lattice Boltzmann methods, input, output, nonfunctional requirements, and, where appropriate, system constraints.\\

@@

\section{Introduction}
Lattice Boltzmann systems are well suited to development as a program family because they fit Parnas’s definition of a program family: “a set of programs whose common properties are so extensive that it is advantageous to study the common properties of the programs before analyzing individual members” \citep{parnas1976design}. Developing such systems as a program family is advantageous because Lattice Boltzmann systems share many common features, or commonalities. Furthermore, when there are differences between systems, the variabilities between them can be systematically considered. The purpose of this document is to record these commonalities and variabilities and show the relationships between them, and thus facilitate the specification and development of Lattice Boltzmann program family members. This document will be valuable in all future phases of system development and analysis. For instance, the requirements documentation for any Lattice Boltzmann systems will use the commonality analysis, since the requirements should refine the commonalities, which are shared requirements of all such systems. Moreover, the design of any future system will use this documentation to facilitate consideration of the variabilities, so that likely changes can be made to the system with a minimal amount of work.

The scope of the commonality analysis presented here can be considered both from the point of view of Lattice Boltzmann systems and from the point of view of software engineering methodologies. From the Lattice Boltzmann system perspective, the starting point for the current document is a commonality analysis. With respect to software engineering methodologies, the scope of the current report is restricted to informal methods, with the intention that the informal requirements will form a starting point for later development and refinement by formal methods.

The first section below provides an overview of the program family of Lattice Boltzmann systems, by reviewing what is involved in a commonality analysis and the basics of Lattice Boltzmann systems. After this, the basic terminology and definitions necessary for understanding the remainder of the document are provided. The definitions include terms used in describing a commonality analysis and terms that are used in defining the characteristics and properties of Lattice Boltzmann methods. The next three sections consist of the lists of commonalities, variabilities and parameters of variation, respectively. These three sections form the heart of the documentation and include an extensive set of cross-references to demonstrate the relationships between the different items. The final section provides information on unresolved issues.

\newpage
\section{Overview}
This section provides both an overview of the process of commonality analysis and of Lattice Boltzmann methods. The subsection on commonality analysis briefly introduces this topic, along with references that can be searched for further information. The subsection on Lattice Boltzmann methods outlines the basics of Lattice Boltzmann methods and of the scope of the commonality analysis.

\subsection{Commonality Analysis}
In some situations it is advantageous to develop a collection of related software products as a program family. The idea is that if the software products are similar enough, then it should be possible to predict what the products have in common, what differs between them and then reuse the common aspects and thus support rapid development of the family members. The idea of program families was introduced by \cite{dijkstra1972} and later investigated by \cite{parnas1976design,parnas1979designing}. More recently, \cite{weiss1997defining, weiss1998commonality, ardis1997defining} has considered the concept of a program family in the context of what he terms Family oriented Abstraction, Specification and Translation (FAST) \citep{cuka1997specifying,weiss1999software}.

In the approach advocated by Weiss, the first step is a commonality analysis. This analysis consists of systematically identifying and documenting the commonalities that all program family members share, the variabilities between family members and the terminology used in describing the family. A commonality analysis provides a systematic way of gaining confidence that a family is worth building and of deciding what the family members will be. A commonality analysis document provides the following benefits \cite{weiss1997defining, weiss1998commonality}:

\begin{enumerate}
	\item A starting point for the design of a domain specific languages (DSL): Once a DSL, or application modelling language, is developed the program family members can be rapidly generated by specifying a given family member using the language.
	\item A basis for a common design for all family members: When the software engineers come to designing the individual family members, they can take advantage of the commonalities to reuse code. Moreover, the variabilities can be considered in the design so that they can be easily accommodated. One approach to the design may be to decompose the system into components that can each be customized by specification of values for its various parameters, where the parameters correspond to the parameters of variation identified in the commonality analysis document.
	\item A historical reference: This document records the important issues concerning the scope and the nature of the family (as well as some unsolved issues) to facilitate the involvement of the participants in maintaining and evolving the family.
	\item A basis for re-engineering a domain: Existing projects may not have been developed using software engineering methodologies. The projects can be systematically reorganized and redesigned with the aid of a commonality analysis to unify the existing products.
	\item A basic training reference for new software developers: This document provides the necessary basic information for a new team-member to understand the family. 
\end{enumerate}

The next section will show that the above uses of the commonality analysis document will be beneficial for the development of a family of Lattice Boltzmann programs. The commonality analysis will benefit all subsequent stages in the software development process. For instance, as mentioned in the introduction, the commonalities will act as requirements that will be the starting point for writing a software requirements specification. The commonalities will be refined into specific requirements by fixing the value of their associated variabilities. The change in the values of the variabilities then corresponds to the change from one program family member to another.

As commonalities and variabilities are requirements, they should express “What” functionalities and qualities the system should have, and not mention “How” these requirements are to be accomplished. That is, the commonalities and variabilities should not involve design decisions. The design decisions will be made after the requirements for a family member have been specified. The one exception to this is system constraints, which are requirements that explicitly make design decisions.

Besides the “What” versus “How” test, there are other tests that can be used to review commonalities and variabilities, as proposed by \cite{weiss1997defining}. One such test is the “what is ruled out” test. This test determines if a commonality or variability actually makes a decision because if no alternatives are ruled out then no decision has really been made. Another test is the “negation” test. If the negation of a decision represents a position that someone might argue for, then the original decision is likely to be meaningful. For instance, the statement that “the software should be reliable” has a negation that no one would likely argue for and thus the statement does not represent a good characterization of a goal for the system.

In \cite{weiss1997defining} the stages of a commonality analysis are described in a systematic way. The stages include the following: prepare, plan, analyze, quantify and review. The stages are completed through the aid of a moderator and a series of meeting and preliminary documents and documentation reviews. The approach adopted here is to revise the original commonality analysis document produced by \cite{chen2003} and then make the new document available to others for review. The new document will be maintained in a concurrent versioning system repository so that multiple authors can work on it, and more importantly, so that the documentation’s revision history can be tracked and the documentation can be rolled back to an earlier version if necessary.

\subsection{Lattice Boltzmann Systems}
Lattice Boltzmann Methods (LBM) are a family of fluid dynamics algorithms for simulating single-phase and multiphase fluid flows, often incorporating additional physical complexities \citep{chen1998lattice}. They consider the behaviours of a collection of particles as a single unit at the mesoscopic scale. These methods predict the positional probability of a collection of particles moving through a lattice structure. Off the shelf (OTS) Lattice Boltzmann Solvers (LBS) allow for a range of fluid and physical model input parameters, computational parameters, and output parameters.

As LBS model fluid dynamics within a boundary using a predefined lattice structure, the methods rely on a two step calculation process. The first process is streaming, where the particles move along the lattice via links. The second process is collision, where energy and momentum is transferred among particles that collide \citep{bao2011lattice}.
There are many standardized lattice models - individual solvers within the family might only use a subset of them.
The LBM uses the initial parameters of the fluid to find the probability of where along the lattice linkages a group of particles are most likely to travel. It then moves the particles into the next node, and transfers the energy and momentum if a collision occurs. Then the process repeats for the duration of the modeling instance.

\newpage
\section{Terminology and Definitions}
This section is divided into two subsections. The first discusses the terminology that comes from the software engineering field, while the second presents the definitions used in Lattice Boltzmann solvers. Common acronyms are also listed in this section. The lists are not intended to be read sequentially, but rather to be consulted for reference purposes; therefore, the terms are ordered alphabetically, with the consequence that some terms that appear early in the list depend on the definitions of later terms.

\subsection{Software Engineering Related Definitions and Acronyms}
\noindent\textbf{Commonality}: A requirement or goal common to all family members.\\

\noindent\textbf{Goal}: “Goals capture, at different levels of abstraction, the various objectives the system under consideration should achieve.” \cite{van2001goal}\\

\noindent\textbf{Program Family}: A set of programs that are analyzed and designed together starting from the initial stages of the software development life-cycle.\\

\noindent\textbf{Requirements}: A software requirement is: \textit{i}) a condition or capability needed by a user to solve a problem or achieve an objective; \textit{ii}) a condition or capability that must be met or possessed by a system or system component to satisfy a contract, standard, specification, or other formally imposed document; or, \textit{iii}) a documented representation of a condition or capability as in the above two definitions. \cite{thayer2000ieee}\\

\noindent\textbf{Variability}: A requirement or goal that varies between family members.

\subsection{Lattice Boltzmann Related Definitions and Acronyms}

\noindent\textbf{1D} 1-Dimensional\\

\noindent\textbf{2D}: 2-Dimensional\\

\noindent\textbf{3D}: 3-Dimensional\\

\noindent\textbf{LBM}: Lattice Boltzmann Methods\\

\noindent\textbf{LBS}: Lattice Boltzmann Solvers\\

\noindent\textbf{Velocity Directions}: The number of links connecting to each lattice node in the chosen model from neighbouring nodes. All nodes in a chosen lattice model will have the same number of links. A single link will connect between two adjacent nodes.

\newpage
\section{Commonalities}\label{comm_sec}

This section lists all the common features among all the potential family members. The commonalities are organized using the following abstraction of the system, which can be used to describe all Lattice Boltzmann systems: input information, then generate the simulation and finally output the results. Section \ref{comm_lbm} describes the commonalities for the simulation step. Section \ref{comm_in} highlights the input information that is required for all Lattice Boltzmann systems. The next section, Section \ref{comm_out}, shows the common features for the output of Lattice Boltzmann systems, such as the requirement that mesh information be written to files. (Although the output information could simply be written to the computer’s memory, in all practical applications it is desirable to have a persistent record of the output that was created.) The final section covers qualities of the system that cannot be classified as input, simulation generation or output. These commonalities are termed nonfunctional requirements of the system. For instance, all systems will have the goal that the response time to a user’s request is small enough to allow the user to focus on his/her problem and to maintain his/her train of thought, without being distracted by excessive waiting time. The commonality in this case is refined by a later variability because the specific requirement on the response time will depend on the intended usage of the mesh generating system.

Each commonality below uses the same structure. All of the commonalities are assigned a unique item number, which takes the form of a natural number with the prefix ``C''. Following this, a description of the commonality is provided along with a list of related variabilities, which are given as hyperlinks that allow navigation of the document to the text describing the variability. Finally, each commonality ends with a summary of the history, including the date of creation and any dates of modification, along with a brief description of the modification. If necessary, a previous version of the document can be obtained by using the concurrent versioning system where the files are stored.

\subsection{Lattice Boltzmann Method Solvers}\label{comm_lbm}
\noindent
\begin{minipage}{\textwidth}
	\renewcommand*{\arraystretch}{1.5}
	\begin{tabular}{| p{\colAwidth} | p{\colBwidth}|}
		\hline
		\bf Item Number& C\refstepcounter{comnum}\thecomnum{}\label{lattice} \\
		\hline
	\end{tabular}\\

	\begin{tabular}{| p{\colAwidth} | p{\colBwidth}|}		
		\hline
		\bf Description & A lattice discretizes a computational domain into a finite number of points. All LBS discretize the computational domain using a regular, evenly spaced grid.\\
		\hline
		\bf Related Variability & \vref{numveldir} \vref{varcolop}\\
		\hline
		\bf History & Created April 1, 2020 \\
		\hline
	\end{tabular}
\end{minipage}\\
~\newline\\
~\newline
\noindent
\begin{minipage}{\textwidth}
	\renewcommand*{\arraystretch}{1.5}
	\begin{tabular}{| p{\colAwidth} | p{\colBwidth}|}
		\hline
		\bf Item Number& C\refstepcounter{comnum}\thecomnum\label{collisionoperator} \\
		\hline
	\end{tabular}\\

	\begin{tabular}{| p{\colAwidth} | p{\colBwidth}|}		
		\hline
		\bf Description & All Lattice Boltzmann versions use a collision operator which concerns collisions between particles.\\
		\hline
		\bf Related Variability & \vref{numveldir} \vref{varcolop}\\
		\hline
		\bf History & Created April 1, 2020\\
		\hline
	\end{tabular}
\end{minipage}\\
~\newline\\
~\newline
\noindent
\begin{minipage}{\textwidth}
	\renewcommand*{\arraystretch}{1.5}
	\begin{tabular}{| p{\colAwidth} | p{\colBwidth}|}
		\hline
		\bf Item Number& C\refstepcounter{comnum}\thecomnum\label{probabilitydensityfunc} \\
		\hline
	\end{tabular}\\

	\begin{tabular}{| p{\colAwidth} | p{\colBwidth}|}		
		\hline
		\bf Description & All Lattice Boltzmann versions user a probability density function to give the probability that fluid has moved into a specific domain.\\
		\hline
		\bf Related Variability & \vref{dimensions}\\
		\hline
		\bf History & Created April 1, 2020\\
		\hline
	\end{tabular}
\end{minipage}\\
~\newline\\
~\newline
\noindent
\begin{minipage}{\textwidth}
	\renewcommand*{\arraystretch}{1.5}
	\begin{tabular}{| p{\colAwidth} | p{\colBwidth}|}
		\hline
		\bf Item Number& C\refstepcounter{comnum}\thecomnum\label{discretizevelocity} \\
		\hline
	\end{tabular}\\

	\begin{tabular}{| p{\colAwidth} | p{\colBwidth}|}		
		\hline
		\bf Description & All Lattice Boltzmann versions discretize velocity into a finite number of directions.\\
		\hline
		\bf Related Variability & \vref{numveldir}\\
		\hline
		\bf History & Created April 1, 2020\\
		\hline
	\end{tabular}
\end{minipage}\\
~\newline\\
~\newline
\noindent
\begin{minipage}{\textwidth}
	\renewcommand*{\arraystretch}{1.5}
	\begin{tabular}{| p{\colAwidth} | p{\colBwidth}|}
		\hline
		\bf Item Number& C\refstepcounter{comnum}\thecomnum\label{relaxationupdate} \\
		\hline
	\end{tabular}\\

	\begin{tabular}{| p{\colAwidth} | p{\colBwidth}|}		
		\hline
		\bf Description & All Lattice Boltzmann versions update the velocity distribution during each LBM iteration.\\
		\hline
		\bf Related Variability & \vref{varrelaxops}\\
		\hline
		\bf History & Created April 1, 2020\\
		\hline
	\end{tabular}
\end{minipage}\\
~\newline\\
~\newline
\noindent
\begin{minipage}{\textwidth}
	\renewcommand*{\arraystretch}{1.5}
	\begin{tabular}{| p{\colAwidth} | p{\colBwidth}|}
		\hline
		\bf Item Number& C\refstepcounter{comnum}\thecomnum\label{equildistfunc} \\
		\hline
	\end{tabular}\\

	\begin{tabular}{| p{\colAwidth} | p{\colBwidth}|}		
		\hline
		\bf Description & Every Lattice Boltzmann version uses an equilibrium distribution function to capture the probability distribution of particles.\\
		\hline
		\bf Related Variability & \vref{varedf} \vref{edfstoreage}\\
		\hline
		\bf History & Created April 1, 2020\\
		\hline
	\end{tabular}
\end{minipage}\\
~\newline\\
~\newline
\noindent
\begin{minipage}{\textwidth}
	\renewcommand*{\arraystretch}{1.5}
	\begin{tabular}{| p{\colAwidth} | p{\colBwidth}|}
		\hline
		\bf Item Number& C\refstepcounter{comnum}\thecomnum\label{Boltzmanntransequ} \\
		\hline
	\end{tabular}\\

	\begin{tabular}{| p{\colAwidth} | p{\colBwidth}|}		
		\hline
		\bf Description & Every Lattice Boltzmann version uses a Boltzmann transport equation to describe the statistical behaviour of a system that does not have collisions.\\
		\hline
		\bf Related Variability & \vref{vartraneq}\\
		\hline
		\bf History & Created April 1, 2020\\
		\hline
	\end{tabular}
\end{minipage}\\
\subsection{Input}\label{comm_in}
\noindent
\begin{minipage}{\textwidth}
	\renewcommand*{\arraystretch}{1.5}
	\begin{tabular}{| p{\colAwidth} | p{\colBwidth}|}
		\hline
		\bf Item Number& C\refstepcounter{comnum}\thecomnum\label{fluidandboundaryinfo} \\
		\hline
	\end{tabular}\\

	\begin{tabular}{| p{\colAwidth} | p{\colBwidth}|}		
		\hline
		\bf Description & The LBS require fluid, model, and boundary information for the problem.\\
		\hline
		\bf Related Variability & \vref{interface} \vref{numberoffluids} \vref{typefluidparm}\\
		\hline
		\bf History & Created April 1, 2020\\
		\hline
	\end{tabular}
\end{minipage}\\
\subsection{Output}\label{comm_out}
\noindent
\begin{minipage}{\textwidth}
	\renewcommand*{\arraystretch}{1.5}
	\begin{tabular}{| p{\colAwidth} | p{\colBwidth}|}
		\hline
		\bf Item Number& C\refstepcounter{comnum}\thecomnum\label{predictionstomemory} \\
		\hline
	\end{tabular}\\

	\begin{tabular}{| p{\colAwidth} | p{\colBwidth}|}		
		\hline
		\bf Description & LBS write fluid parameter predictions to memory.\\
		\hline
		\bf Related Variability & \vref{varvisual} \vref{formatoutput} \\
		\hline
		\bf History & Created April 1, 2020\\
		\hline
	\end{tabular}
\end{minipage}\\
\subsection{Nonfunctional Requirements}\label{comm_nfr}
\noindent
\begin{minipage}{\textwidth}
	\renewcommand*{\arraystretch}{1.5}
	\begin{tabular}{| p{\colAwidth} | p{\colBwidth}|}
		\hline
		\bf Item Number& C\refstepcounter{comnum}\thecomnum\label{precision} \\
		\hline
	\end{tabular}\\
